Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-24 articles/cycle/alps-cycle.tex
Add parameter table from Cordillera cycle paper.

    \begin{table*}
      \caption{%
        Palaeo-temperature proxy records and scaling factors yielding
        temperature offset time-series used to force the ice sheet model
        through the last glacial cycle (Fig.~\ref{fig:timeseries}). $f$
        corresponds to the scaling factor adopted to yield Last Glacial Maximum
        ice limits in the vicinity of mapped end moraines
        (Fig.~\ref{fig:footprints}a), and $[{\Delta}T_{\textrm{TS}}]_{32}^{22}$
        refers to the resulting mean temperature anomaly during the period 32
        to~22\,\unit{ka} after scaling.}
      \label{tab:records}
      %\scalebox{.850}[.850]
      \centerline{\begin{tabular}{lccccccl}
        \toprule
        Record    & Latitude & Longitude & Elev. (m~a.s.l.)
                  & Proxy & $f$ & $[{\Delta}\text{TS}]_{32}^{22}$ (K)
                  & Reference\\
        \midrule
        GRIP      &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
                  &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
                  & 3238
                  & \chem{\delta^{18}O}
                  & 0.46 & $-$7.6  % -16.4126 (before scaling)
                  & \citet{Dansgaard.etal.1993} \\
        EPICA     &  75{\degree}06$^{\prime}$\,S   % 75.1
                  & 123{\degree}21$^{\prime}$\,E   % 123.35
                  & 3233
                  & \chem{\delta^{18}O}
                  & 0.46 & $-$9.5  % -9.2055
                  & \citet{Jouzel.etal.2007} \\
        MD01-2444 &  37{\degree}34$^{\prime}$\,N   % 37.561
                  &  10{\degree}04$^{\prime}$\,W   % -10.142
                  & $-$2637
                  & \chem{U^{K'}_{37}}
                  & 1.84 & $-$8.0  % -4.345625
                  & \citet{Martrat.etal.2007} \\
        \bottomrule
      \end{tabular}}
    \end{table*}

>>>>

    \begin{table*}
      \caption{%
        Parameter values used in the ice sheet model.}
      \label{tab:params}
      \noindent\small\makebox[\textwidth]
      {\begin{tabular}{llrll}
        \toprule

        Not.    & Name & Value & Unit & Source \\

        \midrule
        \multicolumn{2}{l}{{Ice rheology}} \\
        \midrule

        $\rho$  & Ice density
                & 910
                & \unit{kg\,m^{-3}}
                & \citet{Aschwanden.etal.2012} \\

        $g$     & Standard gravity
                & 9.81
                & \unit{m\,s^{-2}}
                & \citet{Aschwanden.etal.2012} \\

        $n$     & Glen exponent
                & 3
                & --
                & \citet{Cuffey.Paterson.2010} \\

        $A_{\mathrm{c}}$   & Ice hardness coefficient cold
                & $3.61\e{-13}$
                & \unit{Pa^{-3}\,s^{-1}}
                & \citet{Paterson.Budd.1982} \\

        $A_{\mathrm{w}}$   & Ice hardness coefficient warm
                & $1.73\e3$
                & \unit{Pa^{-3}\,s^{-1}}
                & \citet{Paterson.Budd.1982} \\

        $Q_{\mathrm{c}}$   & Flow law activation energy cold
                & $6.0\e4$
                & \unit{J\,mol^{-1}}
                & \citet{Paterson.Budd.1982} \\

        $Q_{\mathrm{w}}$   & Flow law activation energy warm
                & $13.9\e4$
                & \unit{J\,mol^{-1}}
                & \citet{Paterson.Budd.1982} \\

        $T_{\mathrm{c}}$   & Flow law critical temperature
                & 263.15
                & \unit{K}
                & \citet{Paterson.Budd.1982} \\

        $f$     & Flow law water fraction coeff.
                & 181.25
                & --
                & \citet{Lliboutry.Duval.1985} \\

        $R$     & Ideal gas constant
                & 8.31441
                & \unit{J\,mol^{-1}\,K^{-1}}
                & -- \\

        $\beta$ & Clapeyron constant
                & $7.9\e{-8}$
                & \unit{K\,Pa^{-1}}
                & \citet{Luthi.etal.2002} \\

        $c_{\mathrm{i}}$   & Ice specific heat capacity
                & 2009
                & \unit{J\,kg^{-1}\,K^{-1}}
                & \citet{Aschwanden.etal.2012} \\

        $c_{\mathrm{w}}$   & Water specific heat capacity
                & 4170
                & \unit{J\,kg^{-1}\,K^{-1}}
                & \citet{Aschwanden.etal.2012} \\

        $k$     & Ice thermal conductivity
                & 2.10
                & \unit{J\,m^{-1}\,K^{-1}\,s^{-1}}
                & \citet{Aschwanden.etal.2012} \\

        $L$     & Water latent heat of fusion
                & $3.34\e5$
                & \unit{J\,kg^{-1}\,K^{-1}}
                & \citet{Aschwanden.etal.2012} \\

        \midrule
        \multicolumn{2}{l}{{Basal sliding}} \\
        \midrule

        $q$     & Pseudo-plastic sliding exponent
                & 0.25
                & --
                & \citet{Aschwanden.etal.2013} \\

        $v_{\text{th}}$& Pseudo-plastic threshold velocity
                & 100.0
                & \unit{m\,a^{-1}}
                & \citet{Aschwanden.etal.2013} \\

        $c_0$   & Till cohesion
                & 0.0
                & Pa
                & \citet{Tulaczyk.etal.2000} \\

        $e_0$   & Till reference void ratio
                & 0.69
                & --
                & \citet{Tulaczyk.etal.2000} \\

        $C_{\mathrm{c}}$   & Till compressibility coefficient
                & 0.12
                & --
                & \citet{Tulaczyk.etal.2000} \\

        $\delta$& Minimum effective pressure ratio
                & 0.02
                & --
                & \citet{Bueler.Pelt.2015} \\

        $W_{\text{max}}$ & Maximal till water thickness
                & 2.0
                & m
                & \citet{Bueler.Pelt.2015} \\

        $b_0$   & Altitude of max. friction angle
                & 0
                & m
                & -- \\

        $b_1$   & Altitude of min. friction angle
                & 200
                & m
                & \citet{Clague.1981} \\

        $\phi_0$& Minimum friction angle
                & 15
                & \degree
                & -- \\

        $\phi_1$& Maximum friction angle
                & 45
                & \degree
                & -- \\

        \midrule
        \multicolumn{2}{l}{{Bedrock and lithosphere}} \\
        \midrule

        $q_{\mathrm{G}}$   & Geothermal heat flux
                & 70.0
                & \unit{mW\,m^{-2}}
                & -- \\

        $\rho_{\mathrm{b}}$& Bedrock density
                & 3300
                & \unit{kg\,m^{-3}}
                & -- \\

        $c_{\mathrm{b}}$   & Bedrock specific heat capacity
                & 1000
                & \unit{J\,kg^{-1}\,K^{-1}}
                & -- \\

        $k_{\mathrm{b}}$   & Bedrock thermal conductivity
                & 3.0
                & \unit{J\,m^{-1}\,K^{-1}\,s^{-1}}
                & -- \\

        $\nu_{\mathrm{m}}$ & Astenosphere viscosity
                & $1\e{19}$
                & \unit{Pa\,s}
                & \citet{James.etal.2009} \\

        $\rho_{\mathrm{l}}$& Lithosphere density
                & 3300
                & \unit{kg\,m^{-3}}
                & \citet{Lingle.Clark.1985} \\

        $D$     & Lithosphere flexural rigidity
                & $5.0\e{24}$
                & \unit{N}
                & \citet{Lingle.Clark.1985} \\

        \midrule
        \multicolumn{2}{l}{{Surface and atmosphere}} \\
        \midrule

        $T_{\mathrm{s}}$   & Temperature of snow precipitation
                & 273.15
                & \unit{K}
                & -- \\

        $T_{\mathrm{r}}$   & Temperature of rain precipitation
                & 275.15
                & \unit{K}
                & -- \\

        $F_{\mathrm{s}}$   & Degree-day factor for snow
                & $3.04\e{-3}$
                & \unit{m\,K^{-1}\,day^{-1}}
                & \citet{Shea.etal.2009} \\

        $F_{\mathrm{i}}$   & Degree-day factor for ice
                & $4.59\e{-3}$
                & \unit{m\,K^{-1}\,day^{-1}}
                & \citet{Shea.etal.2009} \\

        $\gamma$& Air temperature lapse rate
                & $6\e{-3}$
                & \unit{K\,m{-1}}
                & -- \\

        \bottomrule
      \end{tabular}}
    \end{table*}

    \begin{table*}
      \caption{%
        Palaeo-temperature proxy records and scaling factors yielding
        temperature offset time-series used to force the ice sheet model
        through the last glacial cycle (Fig.~\ref{fig:timeseries}). $f$
        corresponds to the scaling factor adopted to yield Last Glacial Maximum
        ice limits in the vicinity of mapped end moraines
        (Fig.~\ref{fig:footprints}a), and $[{\Delta}T_{\textrm{TS}}]_{32}^{22}$
        refers to the resulting mean temperature anomaly during the period 32
        to~22\,\unit{ka} after scaling.}
      \label{tab:records}
      \noindent\small\makebox[\textwidth]
      {\begin{tabular}{lccccccl}
        \toprule

        Record    & Latitude & Longitude & Elev. (m~a.s.l.)
                  & Proxy & $f$ & $[{\Delta}\text{TS}]_{32}^{22}$ (K)
                  & Reference\\

        \midrule

        GRIP      &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
                  &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
                  & 3238
                  & \chem{\delta^{18}O}
                  & 0.46 & $-$7.6  % -16.4126 (before scaling)
                  & \citet{Dansgaard.etal.1993} \\

        EPICA     &  75{\degree}06$^{\prime}$\,S   % 75.1
                  & 123{\degree}21$^{\prime}$\,E   % 123.35
                  & 3233
                  & \chem{\delta^{18}O}
                  & 0.46 & $-$9.5  % -9.2055
                  & \citet{Jouzel.etal.2007} \\

        MD01-2444 &  37{\degree}34$^{\prime}$\,N   % 37.561
                  &  10{\degree}04$^{\prime}$\,W   % -10.142
                  & $-$2637
                  & \chem{U^{K'}_{37}}
                  & 1.84 & $-$8.0  % -4.345625
                  & \citet{Martrat.etal.2007} \\

        \bottomrule
      \end{tabular}}
    \end{table*}
